Working with figure environments in texor

### 2023-07-27 supplement/figure-env/figure-example.tex
Updated Supplementary materials

\section{Summary}

>>>>

\section{Other elements in figure objects}
Figures can also house non-image environments like CodeBlocks and Para. This 
also creates an opportunity to add support for CodeBlock numbering with some
lua filter trickery.
\begin{figure}[htbp]
\begin{center}
\begin{verbatim}
code_in_figure <- function() {
  if (pandoc_version >= 3) {
    print("Code in Figure Supported")
  }
  else {
    print("code in Figure not supported")
  }
}
\end{verbatim}
\caption{ Example Code inside Figure environment}
\label{code:example}
\end{center}
\end{figure}
\section{Summary}
